Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
Fig 3: Caption

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG

@@

%% ------------------------------------------------------------------------------------ %%  
%\subsection{The \redm{}{} cluster catalog}
%    \label{ssec:redmapper}
%    
%    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
%    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
%    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
%    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
%    These authors have developed a well-tested red-sequence cluster finder that has 
%    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
%    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
%    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
%    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
%    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
%    their associated membership probabilities. 
%    Details about the performance of the \redm{}~cluster catalog can be found in 
%    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
%    Several studies have published calibrations between the \redm{}~richness estimate, 
%    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
%    Melchior2016}). 
%    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
%    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
%    The \redm{} catalog therefore helps us group massive central galaxies into 
%    samples with different average \mhalo{}. 
%    We will use the central galaxies of \redm{} clusters 
%    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
%    live in massive halos.
%% ------------------------------------------------------------------------------------ %% 
%
%% ------------------------------------------------------------------------------------ %% 
%  \begin{figure}
%      \centering 
%      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
%      \caption{
%          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
%      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
%      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
%          On average, \mcmodel{} underestimates the total stellar mass of massive 
%          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
%          Vertical histograms indicate the mass difference for galaxies with
%          $11.6<$\logmtot{}$<11.9$. 
%          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
%          function. 
%          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
%          of the total luminosity whereas solid lines correspond to the SMF computed
%          using the total luminosity from our 1-D profile. 
%          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
%          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
%          (red lines).
%          \song{New figure for completeness; Need to update the caption}
%          }
%      \label{fig:mass_complete}
%  \end{figure}

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_mass_diff}
      \caption{              
          \song{New figures to show how \mstar{} changes with different definitions; 
                Need to update the caption.}
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for galaxies with
          $11.6<$\logmtot{}$<11.9$. 
          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
          function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
          of the total luminosity whereas solid lines correspond to the SMF computed
          using the total luminosity from our 1-D profile. 
          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
          (red lines).
          }
      \label{fig:mass_diff}
  \end{figure}

>>>>

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG
% Version 7; MNRAS format; Edited by SH

@@

%% ------------------------------------------------------------------------------------ %%  
%\subsection{The \redm{}{} cluster catalog}
%    \label{ssec:redmapper}
%    
%    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
%    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
%    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
%    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
%    These authors have developed a well-tested red-sequence cluster finder that has 
%    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
%    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
%    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
%    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
%    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
%    their associated membership probabilities. 
%    Details about the performance of the \redm{}~cluster catalog can be found in 
%    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
%    Several studies have published calibrations between the \redm{}~richness estimate, 
%    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
%    Melchior2016}). 
%    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
%    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
%    The \redm{} catalog therefore helps us group massive central galaxies into 
%    samples with different average \mhalo{}. 
%    We will use the central galaxies of \redm{} clusters 
%    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
%    live in massive halos.
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_mass_diff}
      \caption{              
          \textbf{Top:} Difference between \mcmodel{} and \mtot{} for massive
      	  galaxies (grey dots).
      	  The running-median of the mass differences along with the standard deviations
      	  in a series of mass bins are shown in large red, hexagons with error bars. 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for all galaxies (shaded 
          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
          \textbf{Middle:} Difference between \mmax{} and \mtot{} in the same format. 
          The average difference is small (0.02 dex) and does not show 
          clear mass--dependence. 
          \textbf{Bottom:} Difference between the \mtot{} and \mgama{} in the same
          format.  
          Here \mgama{} is based on single-\ser{} model derived from SDSS images. 
          }
      \label{fig:mass_diff}
  \end{figure}
